Discussion

### 2023-03-16 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
deleted some notes
thoughts on states and traits

## Trait character of SVs
From relatively early on in ER research, the question was asked whether the use of certain strategies is habitual, i.e. whether they have a trait character[@GrossJohn2003].
Although 
The individual SVs computed in our CAD paradigm were assessed in the laboratory in a single situation.

Hat das Trait-Charakter?

>>>>

## Trait character of SVs

In order to further assess the relevance of the calculated individual SVs, it would be important to know how stable the values are, i.e. whether they would show trait character.
In other words, do the values we calculate represent a stable value within the individual?
This conclusion cannot be drawn from the present study alone.
The individual SVs computed in our CAD paradigm were assessed in the laboratory in a single situation.
By definition, this represents a state.
As previously noted, personal regulation goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
We belief that these goals, factors and demands also influence individual SVs of ER strategies.
Our data presented in this study support this idea.
However, this also means that SVs should differ according to situational factors (e.g., intensity of stimuli).
It also must be taken into account which ER goals the individuals are pursuing in a particular situation.

has been noted by Wilms and colleagues[@Wilms2020] that situational factors and ER goals should be treated as states.
